Pillar 2 - Topic Modeling

### 2019-02-26 Pillar 2 - Topic Modeling.Rmd
output experiment

@@

  burnin = 500,
  iter   = 2000,
  thin   = 100

@@

  dtm = data_cast,
  topics = n_topics,
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 1L

@@

```{r}
start.time <- Sys.time()

result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))

@@

save(result_descrition,
     file = "Output/LDA_ntopics_description.RDATA")

@@

```{r}
start.time <- Sys.time()

result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 1))

@@

save(result_overview ,
     file = "Output/LDA_ntopics_overview.RDATA")

@@

```{r, eval = F}
start.time <- Sys.time()

result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 155, by = 10))

@@

save(result_manual,
     file = "Output/LDA_ntopics_manual.RDATA")

@@

load("Output/LDA_ntopics_description.RDATA")

load("Output/LDA_ntopics_overview.RDATA")

load("Output/LDA_ntopics_manual.RDATA")

result_descrition %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

@@

```{r LDA fit, cache = TRUE}
n_topics <- 5
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

@@

  LDA_model <- LDA(
    x       = dataset,
    k       = n_topics,
    method  = "Gibbs",
    control = list(
      nstart  = 10,
      seed    = c(1:10),
      best    = TRUE,

      burnin  = 4000,
      iter    = 5000,
      thin    = 500,

      verbose = 1e3,
      save    = 1e3,
      keep    = 1e3)
    )

@@

save(list = list_nam,
     file = "LDA.RDATA")
```

>>>>

```{r setup, include = T}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/")
```

@@

  burnin = 100,
  iter   = 5000,
  thin   = 100

@@

  dtm = data_cast,
  topics = n_topics,
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 4L

@@

```{r description topics, cache = TRUE}
start.time <- Sys.time()

result_description <- d_description_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))

@@

save(result_description,
     file = "Output/LDA_ntopics.RDATA")

@@

```{r overview topics, cache = TRUE}
start.time <- Sys.time()

result_overview <- d_overview_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 100, by = 2))

@@

save(result_overview , result_description,
     file = "Output/LDA_ntopics.RDATA")

@@

```{r manual topics, cache = TRUE}
start.time <- Sys.time()

result_manual <- d_manual_cast %>% my_FindTopicsNumber(n_topics = seq(from = 5, to = 75, by = 5))

@@

save(result_manual, result_overview , result_description,
     file = "Output/LDA_ntopics.RDATA")

@@

load("Output/LDA_ntopics.RDATA")

result_description %>%
  select(-Griffiths2004) %>%
  FindTopicsNumber_plot

@@

```{r LDA fit, cache = TRUE}
n_topics <- 35
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

@@

  LDA_model <- LDA(
    x       = dataset,
    k       = n_topics,
    method  = "Gibbs",
    control = my_control
    )

@@

save(list = list_nam,
     file = "Output/topic_model.RDATA")

save(list = list_nam,
     file = "App/Recommender System/topic_model.RDATA")
```
